UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-08 files/paper/paper.tex
update

\section{Method}
In this section we propose our method for color restoration of underwater images. Depending on depth, lighting
conditions, camera, and location, the amount of distortion an image undergoes can vary.  Because ground truth pairs do
not exist for distorted underwater images, we use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate
a paired dataset of images. CycleGAN has shown success in translating an image from domain $X$ to domain $Y$,
\textit{without} a paired sample. By letting $X$ be a set of underwater images

\subsection{Generative Adversarial Networks}

>>>>

\section{Method}

\subsection{Dataset Generation}
In this section we propose our method for color restoration of underwater images. Depth, lighting conditions, camera
type, and location are all factors that affect the amount of distortion an image undergoes. It is possible that
underwater images with no distortion exist. We let $I^C$ be an underwater image with no distortion, and $I^D$
be the same image with distortion. Our goal is to learn the function $f: I^D \rightarrow I^C$. Becasue of the
difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist.

We use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate $I^D$ from $I^C$, which gives us a paired
dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping
$F: X \rightarrow Y$. Figure 2 shows paired samples generated from CycleGAN. From this paired dataset we train a
generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our generation of
training data, CycleGAN simultaneously learns a mapping $G: Y \rightarrow X$, which is equivalent to $f$. In section
IV we show a comparison with our method.

\subsection{Adversarial Loss}
We introduce a discriminator $D$ in order to

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.7cm}}

   \includegraphics[width=0.8in]{n01496331_175_B} &
   \includegraphics[width=0.8in]{n01664065_4022_B} &
   \includegraphics[width=0.8in]{n01917289_889_B} &
   \includegraphics[width=0.8in]{n01914609_116_B} \\
   \includegraphics[width=0.8in]{n01496331_175_A} &
   \includegraphics[width=0.8in]{n01664065_4022_A} &
   \includegraphics[width=0.8in]{n01917289_889_A} &
   \includegraphics[width=0.8in]{n01914609_116_A} \\

\end{tabular}
\caption{Paired samples of ground truth and distorted images generated by CycleGAN. Top row: Ground truth.
Bottom row: Generated samples.}
\end{figure}
